Tables

### 2020-10-27 tables.Rmd
add rest of table drafts
update ego table

@@

knitr::kable(df %>% select(-Characteristics)) %>% kable_styling(latex_options = 'scale_down')
```

>>>>

# Aggregated visited private HS (2-mode network)

```{r}
df <- readRDS('./assets/tables/table_2mode_agg.RDS')

knitr::kable(df) %>% kable_styling(latex_options = 'scale_down')
```

@@

knitr::kable(df %>% select(-ID, -Characteristics), row.names = F) %>% kable_styling(latex_options = 'scale_down')
```
